Practical Optional Types for Clojure

### 2016-01-07 formal-model.tex
explain absent entries

\figref{main:figure:hmapsyntax}
presents
heterogeneous map types.
The type \HMapgeneric{\mandatory{}}{\absent{}}
contains {\mandatory{}}, a map of \emph{present} entries (mapping keywords to types),
\absent{}, a set of keyword keys that are known to be \emph{absent}
and
tag \completenessmeta{} which is either {\complete{}} (``complete'') if the map is fully specified by \mandatory{},
and {\partial{}} (``partial'') if there are \emph{unknown} entries.
%
The partially specified map of
\clj{lunch} in \egref{example:lunchpartial}
is written
\HMapp{\mandatoryset{\mandatoryentrynoarrow{\Valkw{en}}{\String}, {\mandatoryentrynoarrow{\Valkw{fr}}{\String}}}}{\emptyabsent{}}.
We abbreviate this type as \Lunch in this section.
%
The type of the fully specified map
\clj{breakfast} in \egref{example:breakfastcomplete} elides the absent entries,
written
\HMapc{\mandatoryset{\mandatoryentrynoarrow{\Valkw{en}}{\String}, {\mandatoryentrynoarrow{\Valkw{fr}}{\String}}}}.
We abbreviate this type as \Breakfast in this section.
To ease presentation, 
if an HMap has completeness tag \complete{} then \absent{} implicitly contains all keywords not in the domain of \mandatory{}.
%\HMapcwithabsent{\mandatory{}}{\absent{}} is abbreviated to \HMapc{\mandatory{}}. 
Keys cannot be both present and absent.

>>>>

\figref{main:figure:hmapsyntax}
presents
heterogeneous map types.
The type \HMapgeneric{\mandatory{}}{\absent{}}
contains {\mandatory{}}, a map of \emph{present} entries (mapping keywords to types),
\absent{}, a set of keyword keys that are known to be \emph{absent}
and
tag \completenessmeta{} which is either {\complete{}} (``complete'') if the map is fully specified by \mandatory{},
and {\partial{}} (``partial'') if there are \emph{unknown} entries.
%
The partially specified map of
\clj{lunch} in \egref{example:lunchpartial}
is written
\HMapp{\mandatoryset{\mandatoryentrynoarrow{\Valkw{en}}{\String}, {\mandatoryentrynoarrow{\Valkw{fr}}{\String}}}}{\emptyabsent{}}
(abbreviated \Lunch).
%
The type of the fully specified map
\clj{breakfast} in \egref{example:breakfastcomplete} elides the absent entries,
written
\HMapc{\mandatoryset{\mandatoryentrynoarrow{\Valkw{en}}{\String}, {\mandatoryentrynoarrow{\Valkw{fr}}{\String}}}}
(abbreviated \Breakfast).
To ease presentation, 
if an HMap has completeness tag \complete{} then \absent{} is elided and implicitly contains all keywords not in the domain of 
\mandatory{}---dissociating keys is not modelled, so the set of absent entries otherwise
never grows.
Keys cannot be both present and absent.
%\HMapcwithabsent{\mandatory{}}{\absent{}} is abbreviated to \HMapc{\mandatory{}}.
